\documentclass[12pt,letterpaper]{article}
\usepackage[letterpaper,margin=0.75in]{geometry}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{hyperref}

%Hyperref format
\hypersetup{
	colorlinks=true,	% Hyperlinks are colored
	linkcolor=blue,		% Color of internal links (within document)
	citecolor=blue,	    % Color of internal links to the Reference page (within document)
	urlcolor=blue,		% Color of URLs (external) - default is magenta.
	pdftitle = {cover_letter},
	pdfsubject = {FCA},
	pdfauthor = {Gerardo A. Mazzei Capote},
	pdfkeywords = { },	
}
\usepackage{textcomp} % I think the bullet point shapes come from here
\usepackage[backend=bibtex, sorting=none,maxbibnames=99]{biblatex} %References are numbered per order of use in the text as opposed to alphabetically (default)
\addbibresource{BibTex/mypapers.bib}

\usepackage{tgpagella}% The headerrow command makes a table, this package
					  % Allows us to change the column seperation distance
\setlength{\tabcolsep}{0em} % Change the column seperation distance to 0em

\usepackage{enumitem} % Allows changing the spacing between items in a list
\setlist{nosep} % Change the spacing to zero

\usepackage{endnotes} % Enables the creation of end notes
\renewcommand{\notesname}{} % Remove the word "Notes" from the end notes
\let\enotesize\normalsize % Make endnotes the same size as document


% Create a length variable for the table in skills. It is the text width
% minus the indent
\newlength{\skillswidth}
\setlength{\skillswidth}{\textwidth}
\addtolength{\skillswidth}{-\parindent}

% indentsection style, used for sections that aren't already in lists
% that need indentation to the level of all text in the document
\newenvironment{indentsection}[1]%
{\begin{list}{}%
	{\setlength{\leftmargin}{#1}}%
	\item[]%
}
{\end{list}}

% opposite of above; bump a section back toward the left margin
\newenvironment{unindentsection}[1]%
{\begin{list}{}%
	{\setlength{\leftmargin}{-0.5#1}}%
	\item[]%
}
{\end{list}}

% Create a headerrow command for the header of each skills section
\newcommand{\headerrow}[3]
{\vspace{0.4em}
\noindent
% To get the three items spaced left, center, right, I had to use this funny
% \extracolsep stuff. Got it working though.
\begin{tabular*}{\textwidth}{l @{\extracolsep{\fill}} cr}
	\textbf{#1} & % Title/Postion
	#2 &		  % Company Name
	\textbf{#3}\\ % Employment dates
\end{tabular*}}

%\usepackage{bibentry}
%\nobibliography*

% and the actual content starts here
\begin{document}


\begin{center}
	{\LARGE \textbf{Gerardo Andrés Mazzei Capote}}

	45 N. Randall Ave, Apt. 109\ \ \textbullet
	\ \ Madison, WI- 53715, U.S.A.
	\\
	(608) 622-4643 \ \textbullet
	\ \ mazzeicapote@wisc.edu\\
	\href{https://www.linkedin.com/in/gerardo-mazzei-capote}{linkedin.com/in/gerardo-mazzei-capote}
	
\end{center}
\vspace{-0.5em}
\hrule
\vspace{0.4em}
\vspace{-1em}

\section*{COVER LETTER}
\vspace{0.4em}
October 3rd, 2020
\\
To the Hiring Manager in charge of the Research Engineer position at General Electric:
\\
\\
GE's commitment to invent the future of industry resonates with my drive to aid in the development of highly innovative products and solutions. My name is Gerardo A. Mazzei Capote, and I am a Mechanical Engineer with expertise in a variety of polymer-based additive manufacturing techniques, eager to prove that my profile is very compatible with the position of Research Engineer (non-conventional machining).

I am known between my peers as a highly versatile, motivated, and independent research scientist who can work great in a team. During my graduate studies, I had to tackle a variety of challenges related to part design, fracture mechanics, data analysis, coding, polymer processing, and tool-pathing. In my previous position as teaching and research assistant at the Polymer Engineering Center, my organizational and communicational skills, as well as my eagerness to learn quickly proved to be valuable assets to Prof. Tim Osswald, co-director of the institute. My efforts directly resulted in high ratings from students in multiple classes taught; technical presentations at world-renowned conferences of the likes of SFF, AMUG, and RAPID+TCT; peer-reviewed publications in journals like the Additive Manufacturing journal; and the generation of active funds for the institution through preparation of multi-departmental grants, research ventures, and proposal submissions. I have also successfully managed undergraduate research assistants, and coordinated cooperative projects between universities, industry, and institutes of the likes of BMW, Netzsch, the Technical University of Munich, and the University of Lyon - ENISE. My part design and tool-path expertise has resulted in the development of 3D printed heat exchangers, off-axis production of mechanical coupons, and the manufacturing of a COVID19 protective mask ---a project funded by the Wisconsin Alumni Research Foundation. Finally, my profile offers a blend of both Materials Engineering and Mechanical Engineering, which I believe would fit perfectly with the vision and mission of the Research Engineering position being offered by your company.

GE has consistently been the reference for innovation in many fields for years, and it would be my pleasure to contribute to the growth of such a well-respected company. If my profile interests you, it would be a privilege to discuss details of career opportunities whenever it is convenient for you. Thank you for your time, and I look forward to hearing from you.
\\
\\
Sincerely,
\\
\\
\begin{center}
Gerardo A. Mazzei Capote
\end{center}



\end{document}
